The installation and the setup of the project was performed following the documentation written in the section \textit{Installation Instruction} of the ITD document.
\subsection{Installation Steps}
The steps perfomed in order to configure the environment and to run the project are the following:
\begin{itemize}
        \item Installation and setup of \textbf{\textit{Apache Kafka}}
        \begin{itemize}
            \item Kafka was downloaded from the official website \href{https://kafka.apache.org/downloads}{Apache Kafka} following the installation instruction provided in the official documentation.
            \item The configuration of the \textit{server.properties} file was performed following the istruction provided by the other group.
        \end{itemize}
        \item Installation and setup of \textbf{\textit{SonarQube Server}}
        \begin{itemize}
            \item SonarQube was downloaded from the official website \href{https://www.sonarqube.org/downloads/}{SonarQube} following the installation instruction provided in the official documentation.
            \item The configuration of the \textit{sonar.properties} file was performed following the istruction provided by the other group.
            \item After the installation was perfomed the SonarQube server was started and the web interface was accessed in order to create a \textit{User Token} that was used to authenticate the \textit{SonarScanner}.
        \end{itemize}
        \item Installation and setup of \textbf{\textit{SonarScanner}}
        \begin{itemize}
            \item SonarScanner was downloaded from the official website \href{https://docs.sonarqube.org/latest/analysis/scan/sonarscanner/}{SonarScanner} following the installation instruction provided in the official documentation.
            \item The PATH environment variable was set in order to make the \textit{sonar-scanner} command available by the CKB app at runtime as written in the group instructions.
        \end{itemize}
        \item Installation and setup of \textbf{\textit{PostgreSQL}}
        \begin{itemize}
            \item PostgreSQL was downloaded from the official website \href{https://www.postgresql.org/download/}{PostgreSQL} following the installation instruction provided in the official documentation.
            \item As the ITD document states, two databases were created: one for \textit{Sonar} and another for the \textit{CKB} app.
            \item Moreover there were created two users: one for \textit{Sonar} and another for the \textit{CKB} app.
        \end{itemize}
        \item Installation of \textbf{\textit{Ngrok}}: the installation was performed following the instruction provided in the official documentation.
\end{itemize}