\subsection{Overview}
This section is dedicated to the implementation, integration and test plan. The first part of this section will be dedicated to the identification of the main features of the system and the definition of the components that will be used to implement them. The second part will be dedicated to the integration and testing of the components. The third part will be dedicated to the system testing. The last part will be dedicated to the additional specifications on testing.
\subsection{Implementation plan}
Regarding the implementation plan, the bottom-up approach is a good choice for the implementation of the system.

The bottom-up strategy begins at the granular level, focusing on the creation and development of individual components or modules. Each of these elements is designed and developed in isolation, allowing for a deep focus on functionality and performance. This approach ensures that every component is robust and fully operational before it becomes part of a larger system. 

Once these individual modules are developed, they undergo rigorous testing to identify and rectify any issues early in the development cycle. This early detection of problems is a key advantage, as it significantly reduces the complexity and cost of fixes later on. 

After ensuring the reliability of each component, the process moves to the integration phase. Here, these independently developed modules are gradually assembled to form larger subsystems. This step-by-step assembly allows for careful monitoring of interactions between components, ensuring overall system coherence and performance.

Finally, these subsystems are integrated to complete the overall system or project. This incremental approach not only facilitates detailed scrutiny at each stage but also allows for parallel development of components, accelerating the overall timeline. Additionally, it provides flexibility in adapting to changes or incorporating new technologies as development progresses. 
\subsubsection{Feature identification}
\subsubsection{Component Integration and Testing}
\subsection{System testing}
\subsection{Additional specifications on testing}